---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pRoductivity

<!-- badges: start -->

<!-- badges: end -->

pRoductivity is a packege for Finnish Productivity Board data management
and figure production.

## Installation

You can install pRoductivity from [GitHub](https://github.com/) with:

``` r
devtools::install_github("tuottavuuslautakunta/pRoductivity")
```

```{r, message=FALSE, warning=FALSE}

library(pRoductivity)

```


## Data

Datasets are combined with data-raw/main_data.R Eurostat data is updated
with data-raw/get_eurostat_data_10.R and data-raw/get_eurostat_data.R
OECD data is updated with data-raw/get_oecd_sna.R

### Main datasets

Detailed data: 

* data_main, data from with main industry classification
plus C26 ("C", "C26", "F", "G", "H", "I", "J", "M", "N", "TOTAL").

```{r}

str(data_main)

range(data_main$time)

levels(data_main$nace_r2)

```

* data_main_groups, data with main groupings private, private_ex26,
    manu, manu_ex26, service
    
```{r}

str(data_main_groups)

range(data_main_groups$time)

levels(data_main_groups$nace0)

```

Data with shorter publication lag: 

* data_main10, data with aggregate industry classification ("C", "F", "G-I", "J", "M_N", "TOTAL"). 

```{r}

str(data_main10)

range(data_main10$time)

levels(data_main10$nace_r2)

```

* data_main10_groups, data with main groupings private, manu, service

```{r}

str(data_main10_groups)

range(data_main10_groups$time)

levels(data_main10_groups$nace0)

```

### Eurostat data

#### Annual national accounts

From: \* National accounts aggregates by industry (up to NACE A*64)
(nama_10_a64) and nama_10_a10\
* National accounts employment data by industry (up to NACE A\*64)
(nama_10_a64_e) and nama_10_a10e

##### Misssing dat_eurostat_nace10_imput;

-   Estonia Hours for 1995-1999. Imputed based on persons and 2000.
-   Belgian Hours for 2019. Imputed based on persons and 2018.

##### Missing dat_eurostat_nace_imput:

t-1 for many

Hours based on previous or following hours per persons.

UK: \* Industry data from t-2

Euroarea \* Only from 2000

### OECD data

#### Annual national accounts

Missin data: Japan: - EMP_DC\_\_THS_HW missing: based on SAL_DC ? -
D1\_\_CP_NAC M before 2004 - N and M is missing (in STAN M-N) -
B1G\_\_CLV_NAC and B1G\_\_CLV_NAC for 26

CH: - Hours data is missing from all industries - D1 all missing

CA: - Only from 2007

USA: - EMP_DC\_\_THS_HW missing: based on SAL_DC ? - from 1997,
industries from 1998 - persons from 2000, jobs and hours from 1998 (in
stan also for services from 1998)

New Zealand: - Constant prices series (and more) missing for industies.
(in STAN, but only with t-4 years)

Imputed values:

-   Employment data is extrapolated using linear reggression for USA and
    Japan based on jobs data. For USA 1997-? and for Japan 2015-.
-   USA industries 1997 based on total (TODO)
-   EMP_DC\_\_THS_HW is approximated with EMP_DC\_\_THS_PER x
    SAL_DC\_\_THS_HW / SAL_DC\_\_THS_PER for USA and JAPAN.
-   M and N have been dropped for Japan due to missing values

# Weighting data

Countries used in weighting (from weight_geos): "AT", "BG", "CZ", "DE",
"DK", "EE", "EL", "ES", "FI", "BE", "HU", "LT", "FR", "IT", "NL", "NO",
"PT", "SE", "CY", "PL", "SI", "SK"

# Prodtivity levels

-   data_main10_groups_level

Data from [The GGDC Productivity Level
Database](https://www.rug.nl/ggdc/productivity/pld/) 2005 benchmark is
used to set productivity levels on benchmark year.


